---
title: "tutorial_pck_development"
author: "Niklas"
date: "24 9 2021"
output: html_document
---

# Package Development (John Muschellij)

- Create package
- Initialise with GIT

```{r}
library("available")

available("niktools")
```

## Develop first function (into R/ folder)

```{r}
hello <- function(x){
  print(paste("Hello", x, "this is the world!"))
}
```

## Update DESCRIPTION file manually

Author, License, Name, Description, etc...

```{r}
usethis::use_gpl3_license()
```


## BUILD

Click: Build -> Install and Restart

Build -> Configure build tools:

Generate documentation with Roxygen
Check package "--as-cran"


## Roxygen as code documentation

Code -> Insert Roxygen Skeleton

"Ctrl + Alt + Shift + R"

```{r}

#' My first test function in my first package
#'
#' @param x Character, the name of the person
#'
#' @return The output string: \code{\link{print}}
#' @export
#'
#' @examples
#' hello("Niklas")
#' \dontrun{
#' hello("Steve")
#'}
hello <- function(x){
  print(paste("Hello", x, "this is the world!"))
}
```

Build -> Clean & Rebuild

Now: NAMESPACE and /man are updated.

@export: takes care, that function is exported and useable

# Check package

Build - Check - package


# usethis package

```{r}
# usethis::use_readme_rmd() # adds readme file
devtools::build_readme() # 
```


Use GIT and GITHUB

```{r eval=FALSE}
usethis::use_git()
usethis::use_github()

usethis::create_github_token()
gitcreds::gitcreds_set()
```


